A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-09-03 doc/Paper1/ms.tex
Simulated data figure

\begin{table*}
\begin{tabular}{lll}
\hline
{\bf Parameter} &	{\bf Meaning}			& {\bf Prior}\\
\hline
$\tau_2$	&	Time delay of image 2	&	Cauchy$\left(0, 0.1\tau_{\rm range}\right)T\left(\tau_{\rm min},\tau_{\rm max}\right)$\\
$\{m_1, m_2\}$	&	Mean magnitude for each image	& Uniform$(m_{\rm min}, m_{\rm max})$\\
$\beta$		&	Size of QSO variations		& LogUniform$(\beta_{\rm min}, \beta_{\rm max})$\\
$L_q$		&	Length scale of QSO variations	& LogUniform$(L_{\rm min}, L_{\rm max})$\\
$\{S_1, S_2\}$	&	Size of image-specific variations	& LogUniform$\left(A_{\rm min}, A_{\rm max}\right)$\\
$\{\ell_1, \ell_2\}$ &	Length scale of image-specific variations & LogUniform$(\ell_{\rm min}, \ell_{\rm max})$\\
$\alpha$	&	Smoothness of image-specific variations	& Uniform$(1, 2)$\\
$f_{\rm bad}$	&	Fraction of ``bad'' data points	& Uniform$(0,1)$\\
$\kappa_1$	&	Error-bar boost for ``good'' data & $\frac{1}{2}\delta(\kappa_1 - 1) + \frac{1}{2}$LogUniform$(1,100)$\\
$\kappa_2$	&	Extra error-bar boost for ``bad'' data & LogUniform$(1, 100)$\\
$\{b_i\}_{i=1}^N$ &	Badness hidden variables for each data point & Uniform$(0,1)$\\
\hline
{\bf Derived Parameter} & {\bf Meaning}	&	{\bf Definition}\\
\hline
$S_{q}$	&	Standard deviation of QSO variability	& $\beta\sqrt{L}$\\
$\{a_i\}_{i=1}^N$	&	Errorbar multiplier for each data point & $\left\{\begin{array}{lr}\kappa_1, & b_i > f_{\rm bad}\\ \kappa_1\kappa_2, & b_i \leq f_{\rm bad}\end{array}\right.$\\
\hline
{\bf Data}	&	{\bf Meaning}			& {\bf Sampling Distribution}\\
\hline
$\{Y_1, ..., Y_N\}$ &	Noisy magnitude measurements	& $\mathcal{N}\left(\mathbf{m}(\params), \mathbf{C}(\params)\right)$\\
\hline
{\bf Prior Information} & {\bf Meaning}			&\\
\hline
$N$		&	Number of measurements (all images together)\\
$\{t_1, ..., t_N\}$ &	Measurement times\\
$\{k_1, ..., k_N\}$ &	Flags identifying which image was observed
\end{tabular}
\caption{A full list of parameters, prior information, and data in the
FLOTSAM model. If there are more than two images, extra parameters are
added accordingly.\label{tab:prior}}
\end{table*}

@@

>>>>

\begin{table*}
\begin{tabular}{lll}
\hline
{\bf Parameter} &	{\bf Meaning}			& {\bf Prior}\\
\hline
$\tau_1$	&	Time delay of image 1	&	$\delta(\tau_1 - 0)$\\
$\tau_2$	&	Time delay of image 2	&	Cauchy$\left(0, 0.1\tau_{\rm range}\right)T\left(\tau_{\rm min},\tau_{\rm max}\right)$\\
$m_1$	&	Mean magnitude for image 1	& Uniform$(m_{\rm min}, m_{\rm max})$\\
$m'_2$		&	Magnitude of image 2 relative to image 1	& Cauchy$(0,1)$\\
$\beta$		&	Size of QSO variations		& LogUniform$(\beta_{\rm min}, \beta_{\rm max})$\\
$L_q$		&	Length scale of QSO variations	& LogUniform$(L_{\rm min}, L_{\rm max})$\\
$\{S_1, S_2\}$	&	Size of image-specific variations	& LogUniform$\left(A_{\rm min}, A_{\rm max}\right)$\\
$\{\ell_1, \ell_2\}$ &	Length scale of image-specific variations & LogUniform$(\ell_{\rm min}, \ell_{\rm max})$\\
$\alpha$	&	Smoothness of image-specific variations	& Uniform$(1, 2)$\\
$f_{\rm bad}$	&	Fraction of ``bad'' data points	& Uniform$(0,1)$\\
$\kappa_1$	&	Error-bar boost for ``good'' data & $\frac{1}{2}\delta(\kappa_1 - 1) + \frac{1}{2}$LogUniform$(1,100)$\\
$\kappa_2$	&	Extra error-bar boost for ``bad'' data & LogUniform$(1, 100)$\\
$\{b_i\}_{i=1}^N$ &	Badness hidden variables for each data point & Uniform$(0,1)$\\
\hline
{\bf Derived Parameter} & {\bf Meaning}	&	{\bf Definition}\\
\hline
$m_2$	&	Magnitude of image 2	& $m_1 + m'_2$\\
$S_{q}$	&	Standard deviation of QSO variability	& $\beta\sqrt{L}$\\
$\{a_i\}_{i=1}^N$	&	Errorbar multiplier for each data point & $\left\{\begin{array}{lr}\kappa_1, & b_i > f_{\rm bad}\\ \kappa_1\kappa_2, & b_i \leq f_{\rm bad}\end{array}\right.$\\
\hline
{\bf Data}	&	{\bf Meaning}			& {\bf Sampling Distribution}\\
\hline
$\{Y_1, ..., Y_N\}$ &	Noisy magnitude measurements	& $\mathcal{N}\left(\mathbf{m}(\params), \mathbf{C}(\params)\right)$\\
\hline
{\bf Prior Information} & {\bf Meaning}			&\\
\hline
$N$		&	Number of measurements (all images together)\\
$\{t_1, ..., t_N\}$ &	Measurement times\\
$\{k_1, ..., k_N\}$ &	Flags identifying which image was observed
\end{tabular}
\caption{A full list of parameters, prior information, and data in the
FLOTSAM model. If there are more than two images, extra parameters are
added accordingly.\label{tab:prior}}
\end{table*}

@@

\section{Demonstration on Simulated Data}
In this section we demonstrate the inference methods on simulated data. We
created an ``easy'' data set consisting solely of quasar variability with no
microlensing. Then, a ``hard'' data set was created by adding microlensing
variability. The data consisted of 100 measurements of two images over a time
span of 100 days. The true time delay was $\tau_2 = 10$ days. The two data
sets are plotted in Figure~\ref{fig:sim_data}.

\begin{figure*}
\includegraphics[scale=0.4]{Figures/sim_data.eps}
\caption{\label{fig:sim_data}}
\end{figure*}
